Towards Automated Merging of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-04-30 sattose/paper.tex
Changed the title
Added a thread to validity

\title{Using Refactoring Techniques to Reduce Duplication in Object-Oriented Programming Languages\\- Work in Progress -}

@@

>>>>

\title{Towards Automated Merging of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -}

@@

Another thread to validity is that currently, in a very small number of cases, clone detection might result in a false positive. This is in cases where two lines are equal, but they actually call different methods with the same method signature. In such a case, merging such clones might turn out to change the functionality of the program. We have noted this down as a next step, working on basis of a callgraph instead of just the AST.
